Simple Mediation Example

### 2017-06-13 mediation.Rmd
added some additional estimates to help interpretation of mediation.

  # fill in estimates from functions
  total_effect <- te_mod$coefficients[2]
  cde <- cde_mod$coefficients[2]
  nie <- m_x_mod$coefficients[2]*cde_mod$coefficients[3]
  x_affect_on_m <- m_x_mod$coefficients[2]

  estimates <- cbind(total_effect, cde, x_affect_on_m, nie)
  return(estimates)

>>>>

  # fill in estimates from functions
  total_effect <- te_mod$coefficients[2]
  cde <- cde_mod$coefficients[2]
  nie <- m_x_mod$coefficients[2]*cde_mod$coefficients[3]
  y_on_m <- cde_mod$coefficients[3]
  x_on_m <- m_x_mod$coefficients[2]

  estimates <- cbind(total_effect, cde, nie, x_on_m, y_on_m)
  return(estimates)
